### 2012-01-07 docs/runtime_parameters/runtime_parameters.tex
update + make the table landscape to make things fit better
add shading
add categories to the runtime parameters for documentation purposes. In the _parameters file, the headings define the category for the parameters that follow.  The rp.py script now determines the headers and writes separate tables for each category.

@@

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{3.25in}|l|}
\caption[runtime parameters]{runtime parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

@@

@@

\verb=  barrier_timers  = &   Call a parallel\_barrier before each of the simple timers we have coded in advance.f90.  Might cause a very slight overall performance hit.  &  .false. \\

@@

@@

@@

\verb=  burner_threshold_cutoff  = &   Mass fraction cutoff for burner\_threshold\_species  used in burner threshold  &  1.d-10 \\
\verb=  burner_threshold_species  = &   Name of the species to be used in burner threshold  &  "" \\
\verb=  cflfac  = &   CFL factor to use in the computation of the advection timestep constraint  &  0.5d0 \\
\verb=  cg_verbose  = &   Verbosity of bottom solver  &  0 \\
\verb=  check_base_name  = &   prefix to use in checkpoint file names  &  "chk" \\
\verb=  chk_int  = &   Number of timesteps between writing a checkpoint file  &  0 \\

@@

\verb=  conductivity_constant  = &   the constant conductivity (only applies if the conductivity/constant module is used)  &  1.0d0 \\
\verb=  diag_buf_size  = &   number of timesteps to buffer diagnostic output information before writing (note: not implemented for all problems)  &  10 \\
\verb=  do_alltoallv  = &    &  .false. \\
\verb=  do_burning  = &   turn on (.true.) or off (.false.) burning  &  .true. \\

@@

\verb=  do_heating  = &   use analytic heating  &  .false. \\
\verb=  do_initial_projection  = &   Do the initial projection.  &  .true. \\

@@

\verb=  fixed_dt  = &   Fix the time step.  If -1.0, then use the standard time step.  &  -1.0d0 \\

@@

\verb=  hg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\verb=  hg_dense_stencil  = &   In hgproject, in 2D, use a 9 point Laplacian (.true.) or 5-point Laplacian (.false.).  In 3D, use a 27 point Laplacian (.true.) or 7-point Laplacian (.false.).  &  .true. \\
\verb=  init_divu_iter  = &   Number of initial divu iterations.  &  4 \\
\verb=  init_iter  = &   Number of initial pressure iterations.  &  4 \\
\verb=  init_shrink  = &   the multiplicative factor ($\le 1$) to reduce the initial timestep as computed by the various timestep estimators  &  1.d0 \\
\verb=  job_name  = &   job name printed in output  &  "" \\
\verb=  lUsingNFiles  = &   If .true., use nOutFiles processors to write checkpoint and plotfiles. Fortran has the unfortunate feature of each processor only being able to write out 1-2GB each without crashing.  &  .true. \\

@@

\verb=  max_dt  = &   This is the maximum dt that is allowed  &  1.0d33 \\
\verb=  max_dt_growth  = &   The maximum scale factor that the time step is allowed to grow by per time step.  &  1.1d0 \\
\verb=  max_mg_bottom_nlevels  = &   if mg\_bottom\_solver == 4, then how many mg levels can the bottom solver mgt object have  &  1000 \\
\verb=  max_step  = &   Maximum number of steps in the simulation.  &  1 \\
\verb=  mg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\verb=  mg_verbose  = &   Verbsoity of the multigrid solver, but not the bottom solver.  &  0 \\
\verb=  model_file  = &   input model file  &  "model.hse" \\
\verb=  nOutFiles  = &   If lUsingNFiles = .true., use this many processors to write checkpoint and plotfiles.  Fortran has the unfortunate feature of each processor only being able to write out 1-2GB each without crashing.  &  64 \\
\verb=  nuclear_dt_fac  = &   If $T_{max}^n > T_{max}^{n-1}$ set the new dt =   min[dt, dt*{\tt nuclear\_dt\_fac}*( $T_{max}^{n-1}$ / $(T_{max}^n-T_{max}^{n-1})$ ) ] not checkpoint-compatible yet since it wouldn't be backwards compatible  &  -1.0d0 \\
\verb=  perturb_model  = &   Turn on a perturbation in the initial data.  Problem specific.  &  .false. \\

@@

\verb=  plot_Hext  = &   plot external heating (Hext) in plotfile  &  .false. \\
\verb=  plot_Hnuc  = &   plot nuclear energy generation rate (Hnuc) in plotfile  &  .true. \\
\verb=  plot_ad_excess  = &   plot the adiabatic excess  &  .false. \\
\verb=  plot_base  = &   plot w0\_x, w0\_y, w0\_z, divw0, rho0, rhoh0, h0, and p0 in plotfile  &  .false. \\
\verb=  plot_base_name  = &   prefix to use in plotfile file names  &  "plt" \\
\verb=  plot_cs  = &   plot soundspeed  &  .false. \\
\verb=  plot_deltat  = &   rather than use a plot interval, plot a file after the solution has advanced past plot\_deltat in time  &  -1.d0 \\
\verb=  plot_eta  = &   plot $\etarho$ in plotfile  &  .false. \\
\verb=  plot_gpi  = &   plot pi and grad(pi)  &  .true. \\
\verb=  plot_h_with_use_tfromp  = &   Turn on storing of enthalpy-based quantities in the plotfile when we are running with {\tt use\_tfromp}  &  .true. \\
\verb=  plot_int  = &   plot interval  &  0 \\
\verb=  plot_omegadot  = &   plot omegadot in plotfile  &  .true. \\
\verb=  plot_spec  = &   plot species and omegadot in plotfile  &  .true. \\

@@

\verb=  plot_trac  = &   plot tracers in plotfile  &  .false. \\

@@

\verb=  restart  = &   which file to restart from.  -1 means do not restart  &  -1 \\
\verb=  restart_into_finer  = &   restart and add a level of refinement  &  .false. \\

@@

\verb=  s0_interp_type  = &   The interpolation for filling a cell-centered multifab from a 1D bin-centered array. \newline 1 = piecewise constant; \newline 2 = piecewise linear; \newline 3 = quadratic  &  3 \\
\verb=  s0mac_interp_type  = &   The interpolation for filling an edge based multifab from a 1D bin-centered array. \newline 1 = Interpolate s0 to cell centers (with s0\_interp\_type), then average to edges; \newline 2 = Interpolate s0 to edges directly using linear interpolation; \newline 3 = Interpolate s0 to edges directly using quadratic interpolation.  &  1 \\
\verb=  sdc_iters  = &   how many SDC iteractions to take (requires the code be compiled with {\tt SDC := t}  &  4 \\
\verb=  single_prec_plotfiles  = &    &  .false. \\

@@

\verb=  small_dens  = &    &  1.d-5 \\
\verb=  small_temp  = &    &  5.d6 \\

@@

\verb=  stop_time  = &   simulation stop time  &  -1.d0 \\
\verb=  temp_diffusion_formulation  = &   How to compute the explicit thermal diffusion term.  \newline 1 = in terms of $T$; \newline 2 = in terms of $\rho,p_0,X$.  &  2 \\
\verb=  the_copy_cache_max  = &    Number of boxassoc layouts we keep in memory to avoid having to recompute the boxassoc, which is computationally expensive.  &  50 \\
\verb=  the_knapsack_verbosity  = &   Verbosity of the knapscak processor-to-grid algorithm.  &  .false. \\
\verb=  thermal_diffusion_type  = &   In the thermal diffusion solver, 1 = Crank-Nicholson; 2 = Backward Euler.  &  1 \\

@@

\verb=  use_divu_firstdt  = &   Use the divu constraint when computing the first time step.  &  .false. \\
\verb=  use_eos_coulomb  = &   use the Coulomb corrections between ions (if supported by the EOS)  &  .true. \\

@@

\verb=  use_hypre  = &   use the hypre library  &  .false. \\

@@

\verb=  use_particles  = &   call the particle initialization, advection, etc. routines.  &  .false. \\
\verb=  use_soundspeed_firstdt  = &   Use the soundspeed constraint when computing the first time step.  &  .false. \\

@@

\verb=  use_thermal_diffusion  = &   Use thermal diffusion.  &  .false. \\
\verb=  verbose  = &   General verbosity  &  0 \\
\verb=  w0_interp_type  = &   The interpolation for filling a cell-centered multifab from a 1D edge-centered array. \newline 1 = piecewise constant; \newline 2 = piecewise linear; \newline 3 = quadratic  &  2 \\
\verb=  w0mac_interp_type  = &   The interpolation for putting w0 on edges.  We only compute the normal component. \newline 1 = Interpolate w0 to cell centers (with w0\_interp\_type), then average to edges; \newline 2 = Interpolate w0 to edges directly using linear interpolation; \newline 3 = Interpolate w0 to edges directly using quadratic interpolation; \newline 4 = Interpolate w0 to nodes using linear interpolation, then average to edges.  &  1 \\

@@

>>>>

\begin{landscape}

@@

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ EOS
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

@@

\rowcolor{tableShade}
\verb=  small_dens  = &    &  1.d-5 \\
\verb=  small_temp  = &    &  5.d6 \\
\rowcolor{tableShade}
\verb=  use_eos_coulomb  = &   use the Coulomb corrections between ions (if supported by the EOS)  &  .true. \\

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ SDC
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  sdc_iters  = &   how many SDC iteractions to take (requires the code be compiled with {\tt SDC := t}  &  4 \\

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ algorithm initialization
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  do_initial_projection  = &   Do the initial projection.  &  .true. \\
\verb=  init_divu_iter  = &   Number of initial divu iterations.  &  4 \\
\rowcolor{tableShade}
\verb=  init_iter  = &   Number of initial pressure iterations.  &  4 \\
\verb=  restart  = &   which file to restart from.  -1 means do not restart  &  -1 \\
\rowcolor{tableShade}
\verb=  restart_into_finer  = &   restart and add a level of refinement  &  .false. \\

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ base state mapping
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  s0_interp_type  = &   The interpolation for filling a cell-centered multifab from a 1D bin-centered array. \newline 1 = piecewise constant; \newline 2 = piecewise linear; \newline 3 = quadratic  &  3 \\
\verb=  s0mac_interp_type  = &   The interpolation for filling an edge based multifab from a 1D bin-centered array. \newline 1 = Interpolate s0 to cell centers (with s0\_interp\_type), then average to edges; \newline 2 = Interpolate s0 to edges directly using linear interpolation; \newline 3 = Interpolate s0 to edges directly using quadratic interpolation.  &  1 \\
\rowcolor{tableShade}
\verb=  w0_interp_type  = &   The interpolation for filling a cell-centered multifab from a 1D edge-centered array. \newline 1 = piecewise constant; \newline 2 = piecewise linear; \newline 3 = quadratic  &  2 \\
\verb=  w0mac_interp_type  = &   The interpolation for putting w0 on edges.  We only compute the normal component. \newline 1 = Interpolate w0 to cell centers (with w0\_interp\_type), then average to edges; \newline 2 = Interpolate w0 to edges directly using linear interpolation; \newline 3 = Interpolate w0 to edges directly using quadratic interpolation; \newline 4 = Interpolate w0 to nodes using linear interpolation, then average to edges.  &  1 \\

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ burning
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  burner_threshold_cutoff  = &   Mass fraction cutoff for burner\_threshold\_species  used in burner threshold  &  1.d-10 \\
\verb=  burner_threshold_species  = &   Name of the species to be used in burner threshold  &  "" \\
\rowcolor{tableShade}
\verb=  do_burning  = &   turn on (.true.) or off (.false.) burning  &  .true. \\

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ general MAESTRO
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  barrier_timers  = &   Call a parallel\_barrier before each of the simple timers we have coded in advance.f90.  Might cause a very slight overall performance hit.  &  .false. \\
\verb=  do_alltoallv  = &   use the MPI alltoallv call  &  .false. \\
\rowcolor{tableShade}
\verb=  job_name  = &   job name printed in output  &  "" \\
\verb=  the_knapsack_verbosity  = &   Verbosity of the knapscak processor-to-grid algorithm.  &  .false. \\
\rowcolor{tableShade}
\verb=  verbose  = &   General verbosity  &  0 \\

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ grid
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}

@@

@@

\rowcolor{tableShade}

@@

\rowcolor{tableShade}
\rowcolor{tableShade}
\rowcolor{tableShade}
\rowcolor{tableShade}
\rowcolor{tableShade}
\rowcolor{tableShade}
\rowcolor{tableShade}
\rowcolor{tableShade}
\rowcolor{tableShade}
\rowcolor{tableShade}
\rowcolor{tableShade}
\rowcolor{tableShade}
\rowcolor{tableShade}
\verb=  the_copy_cache_max  = &    Number of boxassoc layouts we keep in memory to avoid having to recompute the boxassoc, which is computationally expensive.  &  25 \\
\rowcolor{tableShade}

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ heating
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  do_heating  = &   use analytic heating  &  .false. \\

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ hydrodynamics
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\rowcolor{tableShade}

@@

@@

\rowcolor{tableShade}

@@

@@

@@

\rowcolor{tableShade}

@@

@@

\rowcolor{tableShade}

@@

@@

\rowcolor{tableShade}

@@

@@

\rowcolor{tableShade}

@@

\rowcolor{tableShade}

@@

@@

\rowcolor{tableShade}

@@

@@

@@

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ linear solvers
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  cg_verbose  = &   Verbosity of bottom solver  &  0 \\
\verb=  hg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\rowcolor{tableShade}
\verb=  hg_dense_stencil  = &   In hgproject, in 2D, use a 9 point Laplacian (.true.) or 5-point Laplacian (.false.).  In 3D, use a 27 point Laplacian (.true.) or 7-point Laplacian (.false.).  &  .true. \\
\verb=  max_mg_bottom_nlevels  = &   if mg\_bottom\_solver == 4, then how many mg levels can the bottom solver mgt object have  &  1000 \\
\rowcolor{tableShade}
\verb=  mg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\verb=  mg_verbose  = &   Verbsoity of the multigrid solver, but not the bottom solver.  &  0 \\
\rowcolor{tableShade}
\verb=  use_hypre  = &   use the hypre library  &  .false. \\

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ output
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  check_base_name  = &   prefix to use in checkpoint file names  &  "chk" \\
\verb=  chk_int  = &   Number of timesteps between writing a checkpoint file  &  0 \\
\rowcolor{tableShade}
\verb=  diag_buf_size  = &   number of timesteps to buffer diagnostic output information before writing (note: not implemented for all problems)  &  10 \\
\verb=  lUsingNFiles  = &   If .true., use nOutFiles processors to write checkpoint and plotfiles. Fortran has the unfortunate feature of each processor only being able to write out 1-2GB each without crashing.  &  .true. \\
\rowcolor{tableShade}
\verb=  nOutFiles  = &   If lUsingNFiles = .true., use this many processors to write checkpoint and plotfiles.  Fortran has the unfortunate feature of each processor only being able to write out 1-2GB each without crashing.  &  64 \\
\verb=  plot_Hext  = &   plot external heating (Hext) in plotfile  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_Hnuc  = &   plot nuclear energy generation rate (Hnuc) in plotfile  &  .true. \\
\verb=  plot_ad_excess  = &   plot the adiabatic excess  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_base  = &   plot w0\_x, w0\_y, w0\_z, divw0, rho0, rhoh0, h0, and p0 in plotfile  &  .false. \\
\verb=  plot_base_name  = &   prefix to use in plotfile file names  &  "plt" \\
\rowcolor{tableShade}
\verb=  plot_cs  = &   plot soundspeed  &  .false. \\
\verb=  plot_deltat  = &   rather than use a plot interval, plot a file after the solution has advanced past plot\_deltat in time  &  -1.d0 \\
\rowcolor{tableShade}
\verb=  plot_eta  = &   plot $\etarho$ in plotfile  &  .false. \\
\verb=  plot_gpi  = &   plot pi and grad(pi)  &  .true. \\
\rowcolor{tableShade}
\verb=  plot_h_with_use_tfromp  = &   Turn on storing of enthalpy-based quantities in the plotfile when we are running with {\tt use\_tfromp}  &  .true. \\
\verb=  plot_int  = &   plot interval  &  0 \\
\rowcolor{tableShade}
\verb=  plot_omegadot  = &   plot omegadot in plotfile  &  .true. \\
\verb=  plot_processors  = &   create a field in the plotfile storing the processor number for each zone  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_spec  = &   plot species and omegadot in plotfile  &  .true. \\
\verb=  plot_trac  = &   plot tracers in plotfile  &  .false. \\
\rowcolor{tableShade}
\verb=  single_prec_plotfiles  = &   store the state data in single precision  &  .false. \\

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ particles
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  store_particle_vels  = &   store the velocity of the particle?  &  .false. \\
\verb=  use_particles  = &   call the particle initialization, advection, etc. routines.  &  .false. \\

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ problem initialization
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  model_file  = &   input model file  &  "model.hse" \\
\verb=  perturb_model  = &   Turn on a perturbation in the initial data.  Problem specific.  &  .false. \\

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ thermal diffusion
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  conductivity_constant  = &   the constant conductivity (only applies if the conductivity/constant module is used)  &  1.0d0 \\
\verb=  temp_diffusion_formulation  = &   How to compute the explicit thermal diffusion term.  \newline 1 = in terms of $T$; \newline 2 = in terms of $\rho,p_0,X$.  &  2 \\
\rowcolor{tableShade}
\verb=  thermal_diffusion_type  = &   In the thermal diffusion solver, 1 = Crank-Nicholson; 2 = Backward Euler.  &  1 \\
\verb=  use_thermal_diffusion  = &   Use thermal diffusion.  &  .false. \\

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[runtime parameters]{ timestepping 
 parameters.} \label{table:runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} & 
       \multicolumn{1}{ c|}{\textbf{description}} & 
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline 
\endfirsthead

\rowcolor{tableShade}
\verb=  cflfac  = &   CFL factor to use in the computation of the advection timestep constraint  &  0.5d0 \\
\verb=  fixed_dt  = &   Fix the time step.  If -1.0, then use the standard time step.  &  -1.0d0 \\
\rowcolor{tableShade}
\verb=  init_shrink  = &   the multiplicative factor ($\le 1$) to reduce the initial timestep as computed by the various timestep estimators  &  1.d0 \\
\verb=  max_dt  = &   This is the maximum dt that is allowed  &  1.0d33 \\
\rowcolor{tableShade}
\verb=  max_dt_growth  = &   The maximum scale factor that the time step is allowed to grow by per time step.  &  1.1d0 \\
\verb=  max_step  = &   Maximum number of steps in the simulation.  &  1 \\
\rowcolor{tableShade}
\verb=  nuclear_dt_fac  = &   If $T_{max}^n > T_{max}^{n-1}$ set the new dt =   min[dt, dt*{\tt nuclear\_dt\_fac}*( $T_{max}^{n-1}$ / $(T_{max}^n-T_{max}^{n-1})$ ) ] for example, {\tt nuclear\_dt\_fac} = 0.01 means don't let the max temp grow more than approximately 1 percent not checkpoint-compatible yet since it wouldn't be backwards compatible  &  -1.0d0 \\
\verb=  small_dt  = &   the minimum allowed timestep -- we abort if dt drops below this value  &  1.d-10 \\
\rowcolor{tableShade}
\verb=  stop_time  = &   simulation stop time  &  -1.d0 \\
\verb=  use_divu_firstdt  = &   Use the divu constraint when computing the first time step.  &  .false. \\
\rowcolor{tableShade}
\verb=  use_soundspeed_firstdt  = &   Use the soundspeed constraint when computing the first time step.  &  .false. \\

\end{landscape}
